An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-04-28 Scrap/EconGrowth-R-Functions.Rnw
sfModel, cdModel now in place.

<<single-factor functions, eval=TRUE>>=
####################
# Returns an nls single-factor model for the country and factor specified.
# factor should be one of "K", "L", "Q", "X", or "U".
##
singleFactorModel <- function(countryAbbrev, factor){
  dataTable <- loadData(countryAbbrev) #Load the data that we need.
  # We'll change the name of the desired column to "f"
  dataTable <- replaceColName(dataTable, factor, "f")
  # Now do the fit.
  lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
  # Some economies need different guesses
  if (countryAbbrev == "IR" && factor == "X"){
    mGuess <- 0.7
  } else {
    # This works for every other combination of country and factor.
    mGuess <- 0.5
  }
  start <- list(lambda=lambdaGuess, m=mGuess)
  # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
  model <- iY ~ exp(lambda*iYear) * f^m
  modelSF <- nls(formula=model, data=dataTable, start = start)
#   model <- iY ~ exp(lambda*iYear) * f^m
#   modelSF <- wrapnls(formula=model, data=dataTable, start=list(lambda=lambdaGuess, m=mGuess))
  return(modelSF)
}

#########################
# Takes the single-factor fitted models and creates per-country predictions for them.
# Returns a data.frame with the predictions.
##
singleFactorPredictions <- function(countryAbbrev, factor){
  # Can't make predictions for any of CN, ZA, SA, IR, TZ, or ZM if we're interested in U
  if (!(haveDataSF(countryAbbrev, factor))){
    #If we don't have data for this combination of countryAbbrev and energyType, 
    # return a column of NAs if the above conditions have been met.
    nRows <- 21 # All of these countries need 21 rows.
    df <- as.data.frame(matrix(NA, ncol = 1, nrow = nRows))
    colnames(df) <- "pred"
    return(df)
  }
  model <- singleFactorModel(countryAbbrev, factor)
  pred <- predict(model) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
  df <- data.frame(pred)
  # Pad with rows as necessary
  df <- padRows(countryAbbrev, df)
  return(df)
}

@@

#################################################
# Calculates parameter estimates and confidence intervals
# for the single factor production function for a given a country.
#
# countryAbbrev is a string containing the 2-letter abbreviation for the country, e.g. "US" or "CN"
# factor is a string, one of "K", "L", "Q", "X", or "U"
#
# returns a data.frame of data for the Cobb-Douglas model. 
# First row is the +95% CI on all parameters
# Second row contains the parameter estimates
# Third row is the -95% CI on all parameters
# Each column has names: lambda and m corresponding to the parameters in the model.
##
singleFactorData <- function(countryAbbrev, factor){
  #First, check to see if we want useful work (U) AND one of the countries for which we don't have data.
  if (!haveDataSF(countryAbbrev, factor)){
    #Return a column of NAs if we don't have data for this factor
    nRows <- 3 # +95% CI, SF, and -95% CI.
    nCols <- 2 # lambda, m
    df <- as.data.frame(matrix(NA, ncol = nCols, nrow = nRows))
    colnames(df) <- c("lambda", "m")
    rownames(df) <- c("+95% CI", "SF", "-95% CI")
    return(df)
  }
  # We have a combination of country and factor for which we have data.
  modelSF <- singleFactorModel(countryAbbrev, factor)
  summarySF <- summary(modelSF) # Gives the nls summary table.
  ciSF <- confint(modelSF, level = ciLevel)  # Calculates confidence intervals for the SF model.
  dofSF <- summarySF$df[2] # Gives the degrees of freedom for the model.
  tvalSF <- qt(ciHalfLevel, df = dofSF)
  #Single factor model
  lambda <- as.numeric(coef(modelSF)["lambda"])
  m <- as.numeric(coef(modelSF)["m"])
  # Combine all estimates and their confidence intervals into data frames with intelligent row names
  estSF <- data.frame(lambda = lambda, m = m)
  row.names(estSF) <- "SF"
  # The [1] subscripts pick off the lower confidence interval
  lowerSF <- data.frame(lambda=ciSF["lambda","2.5%"], 
                        m=ciSF["m", "2.5%"])
  row.names(lowerSF) <- "-95% CI"
  # The [2] subscripts pick off the upper confidence interval
  upperSF <- data.frame(lambda=ciSF["lambda","97.5%"], 
                        m=ciSF["m", "97.5%"])
  row.names(upperSF) <- "+95% CI"
  # Now create the data for a table and return it
  dataSF <- rbind(upperSF, estSF, lowerSF)
  return(dataSF)
}

@@

#########################
# Creates a 3-D wireframe graph with SSE on the vertical axis and 
# lambda and m on the horizontal axes.
# params: 
#   countryAbbrev: 2-letter country code (upper case)
#   factor: the factor of production you want to use in the single-factor model. One of K, L, Q, X, or U
#   showOpt: tells whether or not to show a dot at the optimium point.
##
sf3DSSEGraph <- function(countryAbbrev, factor, showOpt=TRUE){
  # First, make a data.frame with which we want to make predictions
  lambdaSeq <- seq(0.0, 0.05, by=0.01)
  mSeq <- seq(0.0, 1.0, by=0.1)
  newX <- data.frame(expand.grid(lambdaSeq, mSeq))
  colnames(newX) <- c("lambda", "m")
  # Get the actual GDP data
  data <- loadData(countryAbbrev)
  y_act <- data[ ,"iY"] # Pick off the GDP column
  y_act <- data.frame(y_act)
  # Need the model to make predictions
  model <- singleFactorModel(countryAbbrev, factor)
  # Get information about the optimum point, the point where SSE is minimized
  coefs <- coef(model)
  lambda_opt <- coefs["lambda"]
  gamma_opt <- coefs["m"]
  xOpt <- data.frame(lambda=lambda_opt, m=gamma_opt)
  y_opt_pred <- predict(model, xOpt)
  y_opt_pred <- data.frame(y_opt_pred)
  compareDF_opt <- cbind(y_opt_pred, y_act)
  se_opt <- with(compareDF_opt, (y_opt_pred-y_act)^2)
  compareDF_opt <- cbind(compareDF_opt, se_opt)
  sums_opt <- colSums(compareDF_opt)
  sse_opt <- sums_opt[3]
  # Need to name these x, y, and z so that the custom panel will pick them up.
  optPoint <- data.frame(x=lambda_opt, y=gamma_opt, z=sse_opt)
  rownames(optPoint) <- NULL

@@

<<cobb-douglas functions, eval=TRUE>>=
####################
# Returns an nls Cobb-Douglas model (without energy) for the country specified. 
# No energy is included in the function to be fitted.
##
cdModel <- function(countryAbbrev){
  dataTable <- loadData(countryAbbrev) #Load the data that we need.
  # Run the non-linear least squares fit to the data. No energy term desired in the Cobb-Douglas equation.
  # Establish guess values for alpha and lambda.
  lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
  alphaGuess <- 0.7 #0.7 gives good results for all countries.  
  start <- list(lambda=lambdaGuess, alpha=alphaGuess)
  # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
  model <- iY ~ exp(lambda*iYear) * iK^alpha * iL^(1 - alpha)
  modelCD <- nls(formula=model, data=dataTable, start=start,
                 #Include the next 3 lines to fit with constraints.
                 #algorithm = "port",
                 #lower = list(lambda=-Inf, alpha=0),
                 #upper = list(lambda=Inf, alpha=1)
                 )
  return(modelCD)
}

@@

####################
# Returns an nls Cobb-Douglas model for the country specified
# Give an energyType ("Q", "X", or "U") if you want to include an energy term. Supply energyType=NA 
# for a model without energy.
# If you supply a value for the gamma argument, a fit with fixed gamma will be provided.
# This function dispatches to cdModel, cdeModel, or cdFixedGammaModel based on which arguments are specified.
##
cobbDouglasModel <- function(countryAbbrev, energyType, gamma){
  if (is.na(energyType)){
    # Fit the Cobb-Douglas model without energy.
    return(cdModel(countryAbbrev=countryAbbrev))
  }
  if (!missing(gamma)){
    # Fit the Cobb-Douglas model with fixed value of gamma
    return(cdeFixedGammaModel(countryAbbrev=countryAbbrev, energyType=energyType, gamma=gamma))
  }
  # Fit the Cobb-Douglas model with gamma as a free parameter
  return(cdeModel(countryAbbrev=countryAbbrev, energyType=energyType))
}

###############################
# Does a grid search over values of gamma for a CD with energy production function.
# Results are returned as a data.frame with columns of gamma, SSE, lambda, alpha, and beta
##
cdeGridData <- function(countryAbbrev, energyType, gammaGrid){
  gamma <- gammaGrid
  models <- lapply(gamma, cobbDouglasModel, energyType=energyType, countryAbbrev=countryAbbrev)
  SSE <- unlist(lapply(models, function(model){summary(model)$sigma}))
  lambda <- unlist(lapply(models, function(model){coef(model)["lambda"]}))
  alpha <- unlist(lapply(models, function(model){coef(model)["alpha"]}))
  data <- as.data.frame(cbind(gammaGrid, lambda, alpha, SSE))
  row.names(data) <- NULL #eliminates row names, leaving only numbered rows
  colnames(data) <- c("gamma", "lambda", "alpha", "SSE")
  data <- transform(data, beta = 1.0 - alpha - gamma)
  # Now make a column that has the country abbreviation
  nRowsData <- nrow(data) #Gets number of rows in data set
  dfOfCountryAbbrevs <- as.data.frame(matrix(countryAbbrev, ncol=1, nrow=nRowsData))
  colnames(dfOfCountryAbbrevs) <- "Country"
  data <- cbind(data, dfOfCountryAbbrevs) 
  return(data)
}

@@

#########################
# Takes the Cobb-Douglas fitted models and creates per-country predictions for them.
# Returns a data.frame with the predictions.
##
cobbDouglasPredictions <- function(countryAbbrev, energyType){
  # Can't make predictions for any of CN, ZA, SA, IR, TZ, or ZM if we're interested in U
  if (!is.na(energyType)){
    # Consider this replacement only if energyType has been specified.
    if (!(haveDataCD(countryAbbrev, energyType))){
      # If we don't have data for this combination of countryAbbrev and energyType, 
      # return a column of NAs when the above conditions have been met.
      nRows <- 21 # All of these countries need 21 rows.
      df <- as.data.frame(matrix(NA, ncol = 1, nrow = nRows))
      colnames(df) <- "pred"
      return(df)
    }
  }
  model <- cobbDouglasModel(countryAbbrev, energyType)
  pred <- predict(model) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
  df <- data.frame(pred)
  # Pad with rows as necessary
  df <- padRows(countryAbbrev, df)
  return(df)
}

@@

  modelCD <- cobbDouglasModel(countryAbbrev=countryAbbrev, energyType=energyType)

@@

  sfKModels <- lapply(countryAbbrevs, singleFactorModel, factor="K")

@@

  sfLModels <- lapply(countryAbbrevs, singleFactorModel, factor="L")

@@

  sfQModels <- lapply(countryAbbrevs, singleFactorModel, factor="Q")

@@

  sfXModels <- lapply(countryAbbrevs, singleFactorModel, factor="X")

@@

  aicSFu <- cbind(US=AIC(singleFactorModel("US", "U")), 
                  UK=AIC(singleFactorModel("UK", "U")), 
                  JP=AIC(singleFactorModel("JP", "U")),

@@

  cdModels <- lapply(countryAbbrevs, cobbDouglasModel, energyType=NA)
  aicCD <- data.frame(lapply(cdModels, AIC))

@@

  cdQModels <- lapply(countryAbbrevs, cobbDouglasModel, energyType="Q")

@@

  cdXModels <- lapply(countryAbbrevs, cobbDouglasModel, energyType="X")

@@

  aicCDu <- cbind(US=AIC(cobbDouglasModel("US", "U")), 
                  UK=AIC(cobbDouglasModel("UK", "U")), 
                  JP=AIC(cobbDouglasModel("JP", "U")),

@@

<<PartialResidualPlots, eval=TRUE>>=
#############################
# Creates a data.frame containing raw data and residuals for given arguments.
# modelType: one of "CD" or "CES"
# countryAbbrev: the country of interest to you
# energyType: one of "Q", "X", or "U"
##
calcResiduals <- function(countryAbbrev, modelType, energyType){
  # Get the model
  if (modelType == "CD"){
    model <- cdModel(countryAbbrev)  
  } else if (modelType == "CES"){
    model <- cesModelNoEnergy(countryAbbrev)
  } else {
    print(paste("Unknown modelType:", modelType, "in partialResidualPlot."))
    return(NULL)
  }
  # Get the residuals
  resid <- resid(model)
  resid <- data.frame(resid)
  resid <- padRows(countryAbbrev=countryAbbrev, df=resid)
  # Load data
  data <- loadData(countryAbbrev)
  data <- cbind(data, resid)
  # Replace name of column we want with the name "iEToFit"
  data <- replaceColName(dataTable=data, factor=energyType, newName="iEToFit")
  return(data)
}

>>>>

<<single-factor functions, eval=TRUE>>=
####################
# Returns an nls single-factor model for the country and factor specified.
# factor should be one of "K", "L", "Q", "X", or "U".
##
sfModel <- function(countryAbbrev, factor){
  dataTable <- loadData(countryAbbrev) #Load the data that we need.
  # We'll change the name of the desired column to "f"
  dataTable <- replaceColName(dataTable, factor, "f")
  # Now do the fit.
  lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
  # Some economies need different guesses
  if (countryAbbrev == "IR" && factor == "X"){
    mGuess <- 0.7
  } else {
    # This works for every other combination of country and factor.
    mGuess <- 0.5
  }
  start <- list(lambda=lambdaGuess, m=mGuess)
  # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
  model <- iY ~ exp(lambda*iYear) * f^m
  modelSF <- nls(formula=model, data=dataTable, start = start)
#   model <- iY ~ exp(lambda*iYear) * f^m
#   modelSF <- wrapnls(formula=model, data=dataTable, start=list(lambda=lambdaGuess, m=mGuess))
  return(modelSF)
}

#########################
# Takes the single-factor fitted models and creates per-country predictions for them.
# Returns a data.frame with the predictions.
##
singleFactorPredictions <- function(countryAbbrev, factor){
  # Can't make predictions for any of CN, ZA, SA, IR, TZ, or ZM if we're interested in U
  if (!(haveDataSF(countryAbbrev, factor))){
    #If we don't have data for this combination of countryAbbrev and energyType, 
    # return a column of NAs if the above conditions have been met.
    nRows <- 21 # All of these countries need 21 rows.
    df <- as.data.frame(matrix(NA, ncol = 1, nrow = nRows))
    colnames(df) <- "pred"
    return(df)
  }
  model <- sfModel(countryAbbrev, factor)
  pred <- predict(model) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
  df <- data.frame(pred)
  # Pad with rows as necessary
  df <- padRows(countryAbbrev, df)
  return(df)
}

@@

#################################################
# Calculates parameter estimates and confidence intervals
# for the single factor production function for a given a country.
#
# countryAbbrev is a string containing the 2-letter abbreviation for the country, e.g. "US" or "CN"
# factor is a string, one of "K", "L", "Q", "X", or "U"
#
# returns a data.frame of data for the Cobb-Douglas model. 
# First row is the +95% CI on all parameters
# Second row contains the parameter estimates
# Third row is the -95% CI on all parameters
# Each column has names: lambda and m corresponding to the parameters in the model.
##
singleFactorData <- function(countryAbbrev, factor){
  #First, check to see if we want useful work (U) AND one of the countries for which we don't have data.
  if (!haveDataSF(countryAbbrev, factor)){
    #Return a column of NAs if we don't have data for this factor
    nRows <- 3 # +95% CI, SF, and -95% CI.
    nCols <- 2 # lambda, m
    df <- as.data.frame(matrix(NA, ncol = nCols, nrow = nRows))
    colnames(df) <- c("lambda", "m")
    rownames(df) <- c("+95% CI", "SF", "-95% CI")
    return(df)
  }
  # We have a combination of country and factor for which we have data.
  modelSF <- sfModel(countryAbbrev, factor)
  summarySF <- summary(modelSF) # Gives the nls summary table.
  ciSF <- confint(modelSF, level = ciLevel)  # Calculates confidence intervals for the SF model.
  dofSF <- summarySF$df[2] # Gives the degrees of freedom for the model.
  tvalSF <- qt(ciHalfLevel, df = dofSF)
  #Single factor model
  lambda <- as.numeric(coef(modelSF)["lambda"])
  m <- as.numeric(coef(modelSF)["m"])
  # Combine all estimates and their confidence intervals into data frames with intelligent row names
  estSF <- data.frame(lambda = lambda, m = m)
  row.names(estSF) <- "SF"
  # The [1] subscripts pick off the lower confidence interval
  lowerSF <- data.frame(lambda=ciSF["lambda","2.5%"], 
                        m=ciSF["m", "2.5%"])
  row.names(lowerSF) <- "-95% CI"
  # The [2] subscripts pick off the upper confidence interval
  upperSF <- data.frame(lambda=ciSF["lambda","97.5%"], 
                        m=ciSF["m", "97.5%"])
  row.names(upperSF) <- "+95% CI"
  # Now create the data for a table and return it
  dataSF <- rbind(upperSF, estSF, lowerSF)
  return(dataSF)
}

@@

#########################
# Creates a 3-D wireframe graph with SSE on the vertical axis and 
# lambda and m on the horizontal axes.
# params: 
#   countryAbbrev: 2-letter country code (upper case)
#   factor: the factor of production you want to use in the single-factor model. One of K, L, Q, X, or U
#   showOpt: tells whether or not to show a dot at the optimium point.
##
sf3DSSEGraph <- function(countryAbbrev, factor, showOpt=TRUE){
  # First, make a data.frame with which we want to make predictions
  lambdaSeq <- seq(0.0, 0.05, by=0.01)
  mSeq <- seq(0.0, 1.0, by=0.1)
  newX <- data.frame(expand.grid(lambdaSeq, mSeq))
  colnames(newX) <- c("lambda", "m")
  # Get the actual GDP data
  data <- loadData(countryAbbrev)
  y_act <- data[ ,"iY"] # Pick off the GDP column
  y_act <- data.frame(y_act)
  # Need the model to make predictions
  model <- sfModel(countryAbbrev, factor)
  # Get information about the optimum point, the point where SSE is minimized
  coefs <- coef(model)
  lambda_opt <- coefs["lambda"]
  gamma_opt <- coefs["m"]
  xOpt <- data.frame(lambda=lambda_opt, m=gamma_opt)
  y_opt_pred <- predict(model, xOpt)
  y_opt_pred <- data.frame(y_opt_pred)
  compareDF_opt <- cbind(y_opt_pred, y_act)
  se_opt <- with(compareDF_opt, (y_opt_pred-y_act)^2)
  compareDF_opt <- cbind(compareDF_opt, se_opt)
  sums_opt <- colSums(compareDF_opt)
  sse_opt <- sums_opt[3]
  # Need to name these x, y, and z so that the custom panel will pick them up.
  optPoint <- data.frame(x=lambda_opt, y=gamma_opt, z=sse_opt)
  rownames(optPoint) <- NULL

@@

<<cobb-douglas functions, eval=TRUE>>=
####################
# Returns an nls Cobb-Douglas model (without energy) for the country specified. 
# No energy is included in the function to be fitted.
##
cdwoeModel <- function(countryAbbrev){
  dataTable <- loadData(countryAbbrev) #Load the data that we need.
  # Run the non-linear least squares fit to the data. No energy term desired in the Cobb-Douglas equation.
  # Establish guess values for alpha and lambda.
  lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
  alphaGuess <- 0.7 #0.7 gives good results for all countries.  
  start <- list(lambda=lambdaGuess, alpha=alphaGuess)
  # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
  model <- iY ~ exp(lambda*iYear) * iK^alpha * iL^(1 - alpha)
  modelCD <- nls(formula=model, data=dataTable, start=start,
                 #Include the next 3 lines to fit with constraints.
                 #algorithm = "port",
                 #lower = list(lambda=-Inf, alpha=0),
                 #upper = list(lambda=Inf, alpha=1)
                 )
  return(modelCD)
}

@@

####################
# Returns an nls Cobb-Douglas model for the country specified
# Give an energyType ("Q", "X", or "U") if you want to include an energy term. Supply energyType=NA 
# for a model without energy.
# If you supply a value for the gamma argument, a fit with fixed gamma will be provided.
# This function dispatches to cdwoeModel, cdeModel, or cdFixedGammaModel based on which arguments are specified.
##
cdModel <- function(countryAbbrev, energyType, gamma){
  if (is.na(energyType)){
    # Fit the Cobb-Douglas model without energy.
    return(cdwoeModel(countryAbbrev=countryAbbrev))
  }
  if (!missing(gamma)){
    # Fit the Cobb-Douglas model with fixed value of gamma
    return(cdeFixedGammaModel(countryAbbrev=countryAbbrev, energyType=energyType, gamma=gamma))
  }
  # Fit the Cobb-Douglas model with gamma as a free parameter
  return(cdeModel(countryAbbrev=countryAbbrev, energyType=energyType))
}

###############################
# Does a grid search over values of gamma for a CD with energy production function.
# Results are returned as a data.frame with columns of gamma, SSE, lambda, alpha, and beta
##
cdeGridData <- function(countryAbbrev, energyType, gammaGrid){
  gamma <- gammaGrid
  models <- lapply(gamma, cdModel, energyType=energyType, countryAbbrev=countryAbbrev)
  SSE <- unlist(lapply(models, function(model){summary(model)$sigma}))
  lambda <- unlist(lapply(models, function(model){coef(model)["lambda"]}))
  alpha <- unlist(lapply(models, function(model){coef(model)["alpha"]}))
  data <- as.data.frame(cbind(gammaGrid, lambda, alpha, SSE))
  row.names(data) <- NULL #eliminates row names, leaving only numbered rows
  colnames(data) <- c("gamma", "lambda", "alpha", "SSE")
  data <- transform(data, beta = 1.0 - alpha - gamma)
  # Now make a column that has the country abbreviation
  nRowsData <- nrow(data) #Gets number of rows in data set
  dfOfCountryAbbrevs <- as.data.frame(matrix(countryAbbrev, ncol=1, nrow=nRowsData))
  colnames(dfOfCountryAbbrevs) <- "Country"
  data <- cbind(data, dfOfCountryAbbrevs) 
  return(data)
}

@@

#########################
# Takes the Cobb-Douglas fitted models and creates per-country predictions for them.
# Returns a data.frame with the predictions.
##
cobbDouglasPredictions <- function(countryAbbrev, energyType){
  # Can't make predictions for any of CN, ZA, SA, IR, TZ, or ZM if we're interested in U
  if (!is.na(energyType)){
    # Consider this replacement only if energyType has been specified.
    if (!(haveDataCD(countryAbbrev, energyType))){
      # If we don't have data for this combination of countryAbbrev and energyType, 
      # return a column of NAs when the above conditions have been met.
      nRows <- 21 # All of these countries need 21 rows.
      df <- as.data.frame(matrix(NA, ncol = 1, nrow = nRows))
      colnames(df) <- "pred"
      return(df)
    }
  }
  model <- cdModel(countryAbbrev, energyType)
  pred <- predict(model) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
  df <- data.frame(pred)
  # Pad with rows as necessary
  df <- padRows(countryAbbrev, df)
  return(df)
}

@@

  modelCD <- cdModel(countryAbbrev=countryAbbrev, energyType=energyType)

@@

  sfKModels <- lapply(countryAbbrevs, sfModel, factor="K")

@@

  sfLModels <- lapply(countryAbbrevs, sfModel, factor="L")

@@

  sfQModels <- lapply(countryAbbrevs, sfModel, factor="Q")

@@

  sfXModels <- lapply(countryAbbrevs, sfModel, factor="X")

@@

  aicSFu <- cbind(US=AIC(sfModel("US", "U")), 
                  UK=AIC(sfModel("UK", "U")), 
                  JP=AIC(sfModel("JP", "U")),

@@

  cdwoeModels <- lapply(countryAbbrevs, cdModel, energyType=NA)
  aicCD <- data.frame(lapply(cdwoeModels, AIC))

@@

  cdQModels <- lapply(countryAbbrevs, cdModel, energyType="Q")

@@

  cdXModels <- lapply(countryAbbrevs, cdModel, energyType="X")

@@

  aicCDu <- cbind(US=AIC(cdModel("US", "U")), 
                  UK=AIC(cdModel("UK", "U")), 
                  JP=AIC(cdModel("JP", "U")),

@@

<<PartialResidualPlots, eval=TRUE>>=
#############################
# Creates a data.frame containing raw data and residuals for given arguments.
# modelType: one of "CD" or "CES"
# countryAbbrev: the country of interest to you
# energyType: one of "Q", "X", or "U"
##
calcResiduals <- function(countryAbbrev, modelType, energyType){
  # Get the model
  if (modelType == "CD"){
    model <- cdwoeModel(countryAbbrev)  
  } else if (modelType == "CES"){
    model <- cesModelNoEnergy(countryAbbrev)
  } else {
    print(paste("Unknown modelType:", modelType, "in partialResidualPlot."))
    return(NULL)
  }
  # Get the residuals
  resid <- resid(model)
  resid <- data.frame(resid)
  resid <- padRows(countryAbbrev=countryAbbrev, df=resid)
  # Load data
  data <- loadData(countryAbbrev)
  data <- cbind(data, resid)
  # Replace name of column we want with the name "iEToFit"
  data <- replaceColName(dataTable=data, factor=energyType, newName="iEToFit")
  return(data)
}

### 2014-04-28 Seminar/EconGrowthSeminar.Rnw
sfModel, cdModel now in place.

<<Coefs_US_SF>>=
sfUSK <- coef(singleFactorModel("US", "K"))
sfUSL <- coef(singleFactorModel("US", "L"))
sfUSQ <- coef(singleFactorModel("US", "Q"))
sfUSX <- coef(singleFactorModel("US", "X"))
sfUSU <- coef(singleFactorModel("US", "U"))
@
\begin{frame}{Single-factor Predictions for $y$} %----------------------------
  \begin{columns}[c]
    \column{2.2in}
      \begin{center}
        \sfEqn
        \vspace{\baselineskip}

>>>>

<<Coefs_US_SF>>=
sfUSK <- coef(sfModel("US", "K"))
sfUSL <- coef(sfModel("US", "L"))
sfUSQ <- coef(sfModel("US", "Q"))
sfUSX <- coef(sfModel("US", "X"))
sfUSU <- coef(sfModel("US", "U"))
@
\begin{frame}{Single-factor Predictions for $y$} %----------------------------
  \begin{columns}[c]
    \column{2.2in}
      \begin{center}
        \sfEqn
        \vspace{\baselineskip}
